---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/hrbrmstr/hrbrmisc.svg)](https://travis-ci.org/hrbrmstr/hrbrmisc) 
![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/hrbrmisc)](http://cran.r-project.org/web/packages/hrbrmisc) 
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/hrbrmisc)

hrbrmisc is ...

The following functions are implemented:

The following data sets are included:

### News

- Version  released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/hrbrmisc")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(hrbrmisc)

# current verison
packageVersion("hrbrmisc")

```

### Test Results

```{r}
library(hrbrmisc)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
